\sysfull

### 2018-04-15 paper/newCoalescing.tex
correct algo 1
corrct the function calls for the energy blind algo

        \While{$\texttt{true}$}
	        \State $ B_\text{c} \gets B$
	        \While{$ B_\text{c} > 0$}
		        \State \Call{execute\_task}{$T_\texttt{i}$}
		        % \State $W$ \gets \Call{f_\text{weight}}{$T_\texttt{i}$}
		        \State $B_\text{c} \gets B_\text{c} - W$
				\State $H_\text{c} \gets H_\text{c} + W$
	        \EndWhile
	        % \State $B$ \gets \Call{f\_compl}{$\texttt{B},\texttt{H_\text{c}},\texttt{H_\text{p}}$}
	         \State $B \leftarrow $ \Call{$f_\text{reboot}$}{B, $H_\text{c}$,$H_\text{p}$}
	        \State \Call{commit\_to\_fram}{}
        \EndWhile
	\end{algorithmic}
\end{algorithm}
%
%
The likelihood that a task group will complete depends on the total amount of
energy consumed by all tasks in the group, i.e. the size of the dynamic task.
%
A good coalescing strategy must moderate the risk of wasted work and capitalize
on benefits of deferred commits by adapting the target size of the dynamic task
to the energy available at runtime. 
%
To describe the proposed strategies we will use the following parameters:
\begin{itemize}
\item target budget $B$: total number of static tasks to be coalesced.
\item current budget $B_\text{c}$: remaining number of tasks to be coalesced before committing to non-volatile memory; 
\item history $H$: up on reboot, it is the number of executed static tasks between the last two power interrupts. While executing, it is the number of executed static tasks since the last power interrupt.
\end{itemize}

@@

The general structure of the proposed coalescing strategies is summaries in algorithm~\ref{algo:genCoalescing}, where where $H_\text{p}$, $H_\text{c}$, $B$ and $B_\text{c}$ represent past history, current history, target budget and current budget, respectively. $T_\text{i}$ is the i-th task being executed and $W$ is its weight.
A coalescing strategy and its performance are defined by the functions: \\
(i) \emph{$f_\text{reboot}$}: which updates the target budget after a reboot; (ii) \emph{$f_\text{weight}$}: which returns the weight of the task just executed and its unit; (iii) \emph{$f_\text{compl}$}: which updates the target budget after a successful completion of a dynamic coalesced task. The following sections detail the different strategies \sys proposes and the needs that originated from one strategy leading to the conception of another one.

@@

The need for \emph{adaptiveness}, that is coalescing static tasks, can be fulfilled by a naive strategy, having the target budget $B$ to increase by $x$ static tasks after a successful completion of a coalesced task, and to decrease by the same number of tasks upon a reboot. In this case: $f_\text{reboot} = B - x$; $f_\text{weight} =  1$; $f_\text{compl} = B + x$; \\
Due to the linear behavior of the target adaptation, this algorithm is slow in reacting to the changes in energy conditions; the energy required by a coalesced task or the available energy. In particular, this algorithm can experience a large number of \emph{repeated power} failures without forward progress.

>>>>

        \While{$\texttt{true}$}
	        \State $ B_\text{c} \gets B$
	        %
	        \While{$ B_\text{c} > 0$}
		        \State \Call{execute\_task}{$T_\texttt{i}$}
		        \State $W \leftarrow $ \Call{$f_\text{weight}$}{$T_\text{i}$}
		        \State $B_\text{c} \gets B_\text{c} - W$
				\State $H_\text{c} \gets H_\text{c} + W$
	        \EndWhile
	        %
	         \State $B \leftarrow $ \Call{$f_\text{compl}$}{B, $H_\text{c}$,$H_\text{p}$}
	        \State \Call{commit\_to\_fram}{\null}
        \EndWhile
	\end{algorithmic}
\end{algorithm}
%
%
The likelihood that a task group will complete depends on the total amount of
energy consumed by all tasks in the group, i.e. the size of the dynamic task.
%
A good coalescing strategy must moderate the risk of wasted work and capitalize
on benefits of deferred commits by adapting the target size of the dynamic task
to the energy available at runtime. 
%
To describe the proposed strategies we will use the following parameters:
\begin{itemize}
\item target budget $B$: total number of static tasks to be coalesced.
\item current budget $B_\text{c}$: remaining number of tasks to be coalesced before committing to non-volatile memory; 
\item history $H$: up on reboot, it is the number of executed static tasks between the last two power interrupts. While executing, it is the number of executed static tasks since the last power interrupt.
\end{itemize}

@@

The general structure of the proposed coalescing strategies is summaries in algorithm~\ref{algo:genCoalescing}, where where $H_\text{p}$, $H_\text{c}$, $B$ and $B_\text{c}$ represent past history, current history, target budget and current budget, respectively. $T_\text{i}$ is the i-th task being executed and $W$ is its weight.
A coalescing strategy and its performance are defined by the functions:
\begin{itemize}
\item $f_\text{reboot}$: which updates the target budget after a reboot.
\item $f_\text{weight}$: which returns the weight of the task just executed and its unit. 
\item $f_\text{compl}$ : which updates the target budget after a successful completion of a dynamic coalesced task.
\end{itemize}
The following sections detail the different strategies \sys proposes and the needs that originated from one strategy leading to the conception of another one.

@@

The need for \emph{adaptiveness}, that is coalescing static tasks, can be fulfilled by a naive strategy, having the target budget $B$ to increase by $x$ static tasks after a successful completion of a coalesced task, and to decrease by the same number of tasks upon a reboot. In this case: 
\begin{itemize}
\item $f_\text{reboot}(B, H_\text{p}) = B - x $;
\item $f_\text{weight}(T_\text{i}) =  1$; 
\item $f_\text{compl}(B,H_\text{c},H_\text{p}) = B + x$; 
\end{itemize}
Due to the linear behavior of the target adaptation, this algorithm is slow in reacting to the changes in energy conditions; the energy required by a coalesced task or the available energy. In particular, this algorithm can experience a large number of \emph{repeated power} failures without forward progress.
